Earth at night*\\ {\footnotesize \textsuperscript{*}The visualisation of average radiance in specific area}

### 2021-09-16 paper/main.tex
update

\subsection{Oauth github}

this is the explanation

@@

Ansible is a famous open source deployment platform, which is convenient to enable the infrastructure as code (IaC). 
It is the main tool to deploy most of the services in this project. Especially, a single EC2 instance with public 
IP is provided for it. But AWS service has to provision services by aws-cli instead of Ansible itself. There are still 
some libaries providing these functions but mostly are from external part.

>>>>

\subsection{Oauth github}
GitHub's OAuth implementation supports standard authorization code type or OAuth2 device Authorization
for apps that do not have access to a web browser. If you want to skip authorizing your app in
standard method, for example, when testing app, you are able to apply the non-web application flow/
If you want to create an OAuth Application in GitHub, client will need to log into Github, visit
the Applications page under your organisation's settings, click Register 'New Application',
set HomePage URL: Enter the Quay Enterprise URL as the HomePage URL, finally, save your settings by
clicking the Register application button. An OAuth App could be used as an identity provider by enabling
a "Login with GitHub" as for the authenticated user. Do not build an OAuth app if you want your
application to act on a single repository. With the repo OAuth scope, OAuth apps is able to act on
all of the authenticated user's repositories. If you want to register for OAuth application,
in the upper-right corner of any page, click your profile photo, then click Setting, in the
left side bar, click Developer settings, in the left side bar, click OAuth Apps, click New
OAuth App, in Application Name, type the name of your app.OAuth is a standard that apps can
use to provide client applications with 'secure delegated access'. OAuth works over HTTPS and
authorizes devices, APIs, servers, and applications with access tokens rather than credentials,
such as your client ID, yout client secret key. Nowadays, OAuth2 is the most widely used form of
OAuth.

@@

Ansible is a famous open source deployment platform, which is convenient to enable the infrastructure as code (IaC). 
It is the main tool to deploy most of the services in this project. Especially, a single EC2 instance with public 
IP is provided for it. But AWS service has to provision services by aws-cli instead of Ansible itself. There are still 
some libaries providing these functions but mostly are from external part. Ansible does not require
a single controlling machine where orchestration begins. Ansible works against multiple systems in your infrastructure
by selecting portions of Ansible's inventory, stored as edit-able, version-able ASCII text files.
